Cross-disciplinary assessment of statistical guidance provided to authors by influential academic journals

### 2021-09-06 analysis/preliminaryAnalysis.Rmd
Update preliminaryAnalysis.Rmd

```{r load_packages}
library(knitr) # for literate programming
library(tidyverse) # for data munging
library(janitor) # for data munging
library(tidylog) # inline code feedback
library(here) # for finding files
library(assertr) # for testing
library(lemon) # to have axes across all graph facets
library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
library(rmarkdown) # for paged table
```

>>>>

```{r load_packages}
library(knitr) # for literate programming
library(tidyverse) # for data munging
library(janitor) # for data munging
library(tidylog) # inline code feedback
library(here) # for finding files
library(assertr) # for testing
library(pointblank) # for testing
library(lemon) # to have axes across all graph facets
library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
library(rmarkdown) # for paged table
```
